Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance

### 2013-11-17 HRUIofMovingObjects/jrnl_article.tex
Moving objects article: finished all section until results.

In the next section we give an introduction to Capon beamforming for medical ultrasound imaging together with a short introduction to lateral sampling and shift invariance. In Section \ref{sec:capon_LLSI} the local lateral shift-invariance of the Capon beamformer is investigated, before the different methods are presented in Section \ref{sec:methods}.

@@

\section{Background}
\subsection{Beamforming}
The standard form of time domain array beamforming is the delay-and-sum beamformer (DAS):
\begin{align}\label{eq:das}
z[n] = \sum_{m = 0}^{M-1}\vec{w}_m^*\vec{x}_m[n - \Delta_m[n]] = \vec{w}^H\vec{x}[n],
\end{align}
where $M$ is the number of elements or channels in the array, $\Delta_m[n]$ is the per-element focusing and steering delay, and $\vec{w}$ is a weight vector or window function. The weight vector is typically selected in order to trade resolution for a lower side lobe level.

@@

Note that one matrix has to be constructed and inverted for each data vector $\vec{x}[n]$ received by the system. This is indeed computational demanding, but following the innovation in GPU computing, and by applying a novel method in order to reduce the size of the matrix inversion problem \cite{Nilsen2009}, real time processing is now possible \cite{Asen}.

@@

The lateral sampling required in an ultrasound image is given by the combined aperture size on transmit ($D_{tx}$) and receive ($D_{rx}$), and the center frequency ($f_c = c/\lambda$), where $c$ is the speed of sound in the body and $\lambda_c$ is the wavelength of the center frequency. The required Nyquist beam spacing is then \cite{Hergum2007}:
\begin{align}
\Delta < \frac{\lambda_c}{D_{tx} + D_{rx}}. \label{eq:resolution}
\end{align}
If this requirement is not fulfilled the scalloping loss could become visible in the image and the system will no longer be lateral shift-invariant. In an ultrasound image with 256 gray levels and 50 dB dynamic range a 1 dB loss corresponds to 5 gray levels. This is approximately equal to the visibility threshold (Weber fraction of 2\%) for a grayscale image, and so a loss larger than 1dB could be visible to the observer. In our analysis a system would therefore be regarded as lateral shift-invariant if the loss is smaller than this threshold.

In order to visualize the local lateral shift-invariance of a given imaging system, we will use lateral shift-variance plots (LSV-plots), introduced by Hergum \textit{et al.} \cite{Hergum2007}. A LSV-plot is constructed for a given imaging system by imaging a laterally moving point scatterer. For each lateral position the root-mean-square (RMS) is calculated in range, and the resulting beam profiles are stacked to produce an image. The LSV-plots in this paper are displayed as a contour plot with contours on -1, -2, -3, -6, -12 and -24 dB. The maximum for each beam profile is also marked with a black dot. The system is said to be local lateral shift-invariant if the contours are diagonal, hence the diagonals have a loss less than 1 dB.

To further quantify the shift-invariance we have calculated the mean absolute error (MAE) of the maximum point in each beam profile versus $f(x)=x$, and the MAE of the amplitude variation for the same set of points. The first number quantifies the amount of geometric distortion, and the latter quantifies the gain variation or in our case the loss of signal. The maximum amplitude deviation along the max-point trace is also calculated and reported. We present all these numbers together with the LSV-plots.

Fig.\,\ref{fig:das_shiftinvariant} presents a LSV-plot for an imaging system using DAS beamforming with a beam spacing equal to (\ref{eq:resolution}). The red dotted vertical lines indicates the position of tx-rx beam pairs. The point scatterer response has been simulated using Field II \cite{Jensen1992, Jensen1996a} \comment{add table with simulation settings}. We see that the contours are approximately diagonal and therefore we can conclude that the system is locally lateral shift-invariant. The P-MAE and A-MAE are also minimal.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_undersampled2_2x.eps}\label{fig:das_shiftvariant}}
}
\caption{LSV-plots of DAS beamforming. If the contours are diagonal the imaging system is said to be lateral local shif-invariant. Red vertical lines are plotted where tx-rx beams are located. a) Sampling corresponding to (\ref{eq:resolution}). b) Undersampling with a factor two.}
\label{fig:das}
\end{figure*}

\section{Local Lateral Shift-Invariance of the Capon Beamformer}\label{sec:capon_LLSI}
We will now investigate the local lateral shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \cite{Synnevag2009, Asen}. In Fig.\,\ref{fig:capon1}. the same point scatterer response as presented in Fig.\,\ref{fig:das_shiftinvariant} has been weighted with Capon weights calculated using (\ref{eq:capon_weights}) with $L = M/2 = 32$, $K=1$ and $d=1/100$. The set of lateral displacements is constructed in such a way that the center beam is the only one hitting the point scatterer exactly. We see that the scalloping loss is tremendous, and not far from the value predicted by Fig\,\ref{fig:das_capon_beams}. The difference between the predicted and the simulated loss is due to several factors. The most important one being that Fig.\,\ref{fig:das_capon_beams} shows a single frequency whereas the RMS used in Fig.\,\ref{fig:capon1} average a broadband signal in range. For a slice through the center of the pulse the scalloping loss is below -30dB.

The diagonal factor $d$ and the effective adaptive aperture size $L$ can be used to control the mainlobe width of the Capon beamformer. In both extreme cases, $d=\infty$ and $L=1$, the Capon beamformer becomes the DAS beamformer, and will require a beamspacing according to (\ref{eq:resolution}). In Fig.\,\ref{fig:capon2} we show how the scalloping loss is reduced when the amount of diagonal loading is increased. We observe that Fig.\,\ref{fig:capon2} contains the same pattern as present in Fig.\,\ref{fig:das_shiftvariant}. From Fig.\,\ref{fig:capon} it should be obvious that the Capon beamformer either require increased lateral sampling in order to make the imaging system locally lateral shift-invariant, or the resolution has to be reduced to the same level as DAS. It would be unwise to do all the computation involved with Capon beamforming with a high $d$ value and end up with a resolution equal to DAS. However, we see that the diagonal factor can be a useful tool if resolution has to be traded for the need of oversampling. The same is true for the subarray length parameter.

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2.eps}\label{fig:capon1}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=1_2.eps}\label{fig:capon2}
}
}
\caption{...}
\label{fig:capon}
\end{figure*}

\section{Methods}\label{sec:methods}
We will now discuss different ways to improve on the lateral shift-invariance when using the Capon beamformer. From the previous section it should now be clear that we somehow need to increase the lateral sampling to make the Capon imaging system lateral shift invariant. In this section we will investigate how this oversampling should be conducted, how large it needs to be and how the proposed methods will affect the system frame rate and the processing complexity.

\subsection{Oversampling on Transmit}
The straight forward way of obtaining sufficient sampling in an active broadband system is by increasing the number of transmit beams (tx-beams) until (\ref{eq:resolution}) is fulfilled. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the lateral sampling on transmit by a factor four and ten respectively. As expected the scalloping loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed compared to Fig.\,\ref{fig:capon} in order to better see the beam-to-beam variation.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_a}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_10x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_b}
}
}
\caption{Oversampling on transmit ...}
\label{fig:capon_oversampling}
\end{figure*}

\subsection{Oversampling by Parallel Receive Beamforming}
Parallel receive beamforming (PRB) means that multiple narrow receive beams (rx-beams) are constructed from one broad tx-beam. Then, by reducing the number of tx-beams and relying on multiple rx-beams in order to get sufficient sampling on receive, it is possible to achieve high frame rates in e.g. cardiac ultrasound imaging. However, PRB also introduce motion artifacts in the image which to some degree can be compensated for \cite{Hergum2007} \comment{cite Bastien}. In (\comment{Cite paper where they use STB + Capon if its out}) it is shown that synthetic transmit beamforming (STB) \cite{Hergum2007} works with Capon beamforming. In \cite{Asen} we also used STB in order to increase the beam density of a cardiac ultrasound recording. In this paper we will consider PRB as being equal to oversampling on transmit when it comes to image quality.

In cardiac ultrasound imaging, PRB is typically used in order to keep the number of rx-beams while the number of tx-beams are reduced. When using PRB for oversampling we would like to keep the number of tx-beams while the number of rx-beams are increased. The acquisition frame rate will then not be affected. On the other hand PRB will also increase the number of covariance matrices, and thereby the number of matrix-inversions with a factor equal to the number of parallel receive lines. The processing times reported in \cite{Asen} will then also increase with a factor equal to the number of parallel receive lines. Since almost 10x oversampling is required in order to achieve lateral shift invariant imaging of a moving point scatterer, non of the implementations described in \cite{Asen} would be real time any more.

One possible solution is to estimate the covariance matrix from multiple beams \cite{Jensen2012}, making one covariance matrix per range.  Tailoring the method of Jensen and Austeng to cardiac ultrasound imaging it makes more sense to construct one covariance matrix per tx-beam using multiple parallel rx-beams. This solution would then not increase the number of inversions needed, but the time taken to construct the matrices would increase. We will not investigate this method further in this paper.

\subsection{Oversampling by Phase Rotation}
The Capon beamformer formula in (\ref{eq:capon_weights}) gives a direct opportunity for oversampling using phase rotation. The steering vector $\vec{a}$ has in previous work been set to $\vec{1}$ since the ultrasound data are pre-delayed. However, the steering vector can also, as in narrow band applications, be varied over a set of pre-defined vectors. In a narrow band setting the beam can make a sweep across the whole sector by only using phase rotation. This is also possible in broadband applications as long as the phase rotation is limited to a fraction of the wave length. It is therefore possible to make a sweep between the current beam and its neighbours using only phase rotation.

@@

\comment{Add phase rotation formula.}

\comment{Discuss different ways of selecting angles}

\comment{Phase rotation version of STB.}

\begin{figure*}[!t]
	\centerline{
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_oversampling_2_PR_zoomed.eps}
		}
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_10x_oversampling_2_zoomed_PR.eps}
		}
	}
	\caption{Oversampling using phase rotation ...}
	\label{fig:benchmark_capon_bs}
\end{figure*}

@@

\subsection{In-Vivo Images}
Investigate if phase rotation improves contrast in in-vivo images of the heart.

@@

Other methods claiming super resolution would also need some degree of oversampling (Eigenspace, LCA etc.).

@@

Oversampling is not only essential to keep the amplitude level of bright point scatterers it will also help to improve contrast and edge definitions. If oversampling is not applied the edge delineation of an moving object will fluctuate in the same way as a moving point scatterer.

TODO: Add citations – Hergum/Bjåstad Local shift invariance and MLA’s… Is there any publications stating that Capon do not work on moving objects?

>>>>

In the next section we give an introduction to Capon beamforming for medical ultrasound imaging together with a short introduction to lateral sampling and shift invariance. In Section \ref{sec:capon_LLSI} the local lateral shift-invariance of the Capon beamformer is investigated, before the different methods are presented in Section \ref{sec:methods}. Then, in Section \ref{sec:res} and Section \ref{sec:dis} we present and discuss the results of applying the phase rotation method on \textit{in-vitro} data . Finally we give our conclusion in Section \ref{sec:con}.

@@

\section{Background}
\subsection{Standard Beamforming}
The standard form of time domain array beamforming is the delay-and-sum beamformer (DAS) where the output $z$ is calculated as:
\begin{align}\label{eq:das}
z[n] = \sum_{m = 0}^{M-1}\vec{w}_m^*\vec{x}_m[n - \Delta_m[n]] = \vec{w}^H\vec{x}[n],
\end{align}
where $M$ is the number of elements or channels in the array, $\Delta_m[n]$ is the per-element focusing and steering delay, and $\vec{w}$ is a weight vector or window function. The weight vector is typically selected in order to trade resolution for a lower side lobe level. Hence, the weights are typically real and their K-space response is then symmetric.

@@

Note that one matrix has to be constructed and inverted for each data vector $\vec{x}[n]$ received by the system. This is indeed computational demanding, but following the innovation in GPU computing, and by applying a novel method in order to reduce the size of the matrix inversion problem \cite{Nilsen2009}, real time processing is now possible \cite{Asen}. From (\ref{eq:capon_weights} it is clear that complex data will result in complex weights. The weights can therefore have an asymmetric K-space response which basically means that zeros does not have to be symmetric and that the beam can be micro-steered by phase rotation.

@@

The lateral sampling required in an ultrasound image is given by the combined aperture size on transmit ($D_{tx}$) and receive ($D_{rx}$), and the center frequency ($f_c = c/\lambda$), where $c$ is the speed of sound in the body and $\lambda_c$ is the wavelength of the center frequency. The required Nyquist beam spacing is then \cite{Hergum2007}:
\begin{align}
\Delta < \frac{\lambda_c}{D_{tx} + D_{rx}}. \label{eq:resolution}
\end{align}
If this requirement is not fulfilled the scalloping loss could become visible in the image and the system will no longer be lateral shift-invariant. In an ultrasound image with 256 gray levels and 50 dB dynamic range a 1 dB loss corresponds to 5 gray levels. This is approximately equal to the visibility threshold (Weber fraction of 2\%) for a grayscale image, and a loss larger than 1dB could therefore end up being visible to the observer. In our analysis a system would, based on this reasoning, be regarded as lateral shift-invariant if the loss is smaller than 1 dB. However, depending on light conditions and e.g. the selected gray level mapping, a larger loss might be acceptable.

In order to visualize the local lateral shift-invariance of a given imaging system, we will make use of lateral shift-variance plots (LSV-plots), introduced by Hergum \textit{et al.} \cite{Hergum2007}. A LSV-plot is constructed for a given imaging system by imaging a laterally moving point scatterer. For each lateral position the root-mean-square (RMS) is calculated in range, and the resulting beam profiles are stacked to produce an image. The LSV-plots in this paper are displayed as a contour plot with contours on -1, -2, -3, -6, -12 and -24 dB. The maximum for each beam profile is also marked with a black dot. The system is said to be local lateral shift-invariant if the contours are diagonal, hence the diagonals have a loss less than 1 dB.

To further quantify the shift-invariance we have calculated the mean absolute error (MAE) of the maximum point in each beam profile versus $f(x)=x$ (P-MAE), and the MAE of the amplitude variation for the same set of points (A-MAE). The first number quantifies the amount of geometric distortion, and the latter quantifies the gain variation or in our case the loss of signal. The maximum amplitude deviation along the max-point trace is also calculated and reported. We present all these numbers together with the LSV-plots.

Fig.\,\ref{fig:das_shiftinvariant} presents a LSV-plot for an imaging system using DAS beamforming with a beam spacing equal to (\ref{eq:resolution}). The red dotted vertical lines indicates the position of tx-rx beam pairs. The point scatterer response has been simulated using Field II \cite{Jensen1992, Jensen1996a} \comment{add table with simulation settings or just insert in text?}. We see that the contours are approximately diagonal and therefore we can conclude that the system is locally lateral shift-invariant. The P-MAE and A-MAE are also minimal.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_normal2.eps}\label{fig:das_shiftinvariant}}
\hfill{}
\subfloat[]{\includegraphics[width=0.5\linewidth]{\img das_undersampled2_2x.eps}\label{fig:das_shiftvariant}}
}
\caption{LSV-plots of DAS beamforming. If the contours are diagonal the imaging system is said to be lateral local shif-invariant. Red vertical lines are plotted where transmit-receive beam pairs are located. a) Sampling corresponding to (\ref{eq:resolution}). The system is locally lateral shift-invariant. b) Undersampling with a factor two. The system is no longer locally lateral shift-invariant.}
\label{fig:das}
\end{figure*}

\section{Local Lateral Shift-Invariance of the Capon Beamformer}\label{sec:capon_LLSI}
We will now investigate the local lateral shift-invariance of the Capon beamformer with parameters equal to the once used in earlier work \cite{Synnevag2009, Asen}. In Fig.\,\ref{fig:capon1}. the same point scatterer response as presented in Fig.\,\ref{fig:das_shiftinvariant} has been weighted with Capon weights calculated using (\ref{eq:capon_weights}) with $L = M/2 = 32$, $K=1$ and $d=1/100$. The set of lateral displacements is constructed in such a way that the center beam is the only one hitting the point scatterer exactly. We see that the scalloping loss is tremendous, and not far from the value predicted by Fig\,\ref{fig:das_capon_beams}. The difference between the predicted and the simulated loss might be caused by several factors. The most important one being that Fig.\,\ref{fig:das_capon_beams} shows a single frequency whereas the RMS used in Fig.\,\ref{fig:capon1} average a broadband signal in range. For a slice through the center of the pulse the scalloping loss is below -30dB.

The diagonal factor $d$ and the effective adaptive aperture size $L$ can be used to control the mainlobe width of the Capon beamformer. In both extreme cases, $d\gg1$ and $L=1$, the Capon beamformer becomes the DAS beamformer, and will require a beamspacing according to (\ref{eq:resolution}). In Fig.\,\ref{fig:capon2} we show how the scalloping loss is reduced when the amount of diagonal loading is increased. We observe that Fig.\,\ref{fig:capon2} contains the same pattern as present in Fig.\,\ref{fig:das_shiftvariant}. From Fig.\,\ref{fig:capon} it should be obvious that the Capon beamformer either require increased lateral sampling in order to make the imaging system locally lateral shift-invariant, or the resolution has to be reduced to the same level as DAS. It would be unwise to do all the computation involved with Capon beamforming with a high $d$ value and end up with a resolution equal to DAS. However, we see that the diagonal factor can be a useful tool if resolution has to be traded for the need of oversampling. The same is true for the subarray length parameter.

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2.eps}\label{fig:capon1}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=1_2.eps}\label{fig:capon2}
}
}
\caption{LSV-plots of Capon beamforming with $L=M/2=32$ and $K=1$, and with sampling corresponding to (\ref{eq:resolution}) a) The diagonal loading factor $d=1/100$. The system is not locally lateral shift-invariant. b) The diagonal loading factor $d$ is increased to 1. The system is still not locally lateral shift-invariant.}
\label{fig:capon}
\end{figure*}

\section{Methods}\label{sec:methods}
We will now discuss different ways to improve on the lateral shift-invariance when the Capon beamformer is used. From the previous section it should be clear that we somehow need to increase the lateral sampling to make the Capon imaging system locally lateral shift-invariant. In this section we will investigate how this oversampling should be conducted, how large it needs to be and how the proposed methods will affect the system frame rate and the processing complexity.

\subsection{Oversampling on Transmit}
The straight forward way of obtaining sufficient sampling in an active system is by increasing the number of transmit beams (tx-beams) until (\ref{eq:resolution}) is fulfilled or the LSV-plot has a uniform level along the diagonals. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the lateral sampling on transmit by a factor of four and ten respectively. As expected the scalloping loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed compared to Fig.\,\ref{fig:capon} in order to better see the beam-to-beam variation.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_a}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_10x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_b}
}
}
\caption{Capon beamforming as described in Fig\,\ref{fig:capon} with oversampling on transmit. The figure is zoomed compared with Fig\,\ref{fig:capon} to better see the beam-to-beam variation. a) 4x oversampling. b) 10x oversampling.}
\label{fig:capon_oversampling}
\end{figure*}

\subsection{Oversampling by Parallel Receive Beamforming}
Parallel receive beamforming (PRB) means that multiple narrow receive beams (rx-beams) are constructed from one broad tx-beam. Then, by reducing the number of tx-beams and relying on multiple rx-beams in order to get sufficient sampling on receive, it is possible to achieve high frame rates in e.g. cardiac ultrasound imaging. However, PRB also introduce motion artifacts in the image which to some degree can be compensated for \cite{Hergum2007} \comment{cite Bastien}. In (\comment{Cite paper where they use STB + Capon if its out}) it is shown that synthetic transmit beamforming (STB) \cite{Hergum2007} works with Capon beamforming. In \cite{Asen} we also used STB in order to increase the beam density of a cardiac ultrasound recording. In this discussion we consider PRB as being equal to oversampling on transmit when it comes to image quality.

In cardiac ultrasound imaging, PRB is typically used in order to keep the number of rx-beams while the number of tx-beams are reduced. When using PRB for oversampling we would like to keep the number of tx-beams while the number of rx-beams are increased. The acquisition frame rate will then not be affected. On the other hand more rx-beams will increase the number of covariance matrices, and thereby the number of matrix-inversions with a factor equal to the number of parallel receive lines. The processing times reported in \cite{Asen} will then also increase with a factor equal to the number of parallel receive lines. Since almost 10x oversampling is required in order to achieve lateral shift invariant imaging of a moving point scatterer, non of the implementations described in \cite{Asen} would be real time any more.

One possible solution is to estimate the covariance matrix from multiple beams \cite{Jensen2012}, generating one covariance matrix per range.  Tailoring the method of Jensen and Austeng to cardiac ultrasound imaging it makes more sense to construct one covariance matrix per tx-beam using multiple parallel rx-beams. This solution will not increase the number of matrix inversions, but the time taken to construct the matrices will increase. We will not investigate this method further in this paper. \comment{Kanskje litt dumt å nevne det da...?}

\subsection{Oversampling by Phase Rotation}
The Capon beamformer formula in (\ref{eq:capon_weights}) gives a direct opportunity for oversampling using phase rotation. The steering vector $\vec{a}$ has in previous work been set to $\vec{1}$ since the ultrasound data are pre-delayed. However, the steering vector can also, as in narrow band applications, be varied over a set of pre-defined vectors. In a narrow band setting the beam can make a sweep across the whole sector by only using phase rotation. This is also possible in broadband applications as long as the phase rotation is limited to a fraction of the wave length. It is therefore possible to make a sweep between the current beam and its neighbours using only phase rotation. Phase rotation is what the Capon beamformer use internally to micro-steer away from bright point scatterers and to enhance cyst edges.

@@

The steering angles can be spread out in many different ways. If the number of steering angles is $N_\theta$ we have selected a uniform distribution of $\theta$  with $N_\theta/2$ angles on each side of the original steering direction if $N_\theta$ is even, and $(N_\theta-1)/2$ if $N_\theta$ is odd.

Oversampling by phase rotation introduce similar block artifacts as PRB, but on a smaller scale. These artifacts could be removed if we distributes our steering angles as beams are spread out for the STB technique. We then get a phase rotation version of STB where e.g. eight phase rotated beams are averaged into four. \comment{Move to discussion?}

\begin{figure*}[!t]
	\centerline{
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_oversampling_2_PR_zoomed.eps}
		}
		\subfloat[]{
			\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_10x_oversampling_2_zoomed_PR.eps}
		}
	}
	\caption{Capon beamforming as described in Fig\,\ref{fig:capon} with oversampling based on phase rotation. The figure is zoomed compared with Fig\,\ref{fig:capon} to better see the beam-to-beam variation. a) 4x oversampling. b) 10x oversampling.}
	\label{fig:benchmark_capon_bs}
\end{figure*}

@@

\subsection{In-Vivo Images}
Investigate if phase rotation improves contrast in in-vivo images of the heart or liver.

@@

Other methods claiming super resolution would also need oversampling (Eigenspace, LCA etc.) to some extent.

@@

Oversampling is not only essential to keep the amplitude level of bright point scatterers it will also helps to improve contrast and edge definitions. If oversampling is not applied the edge delineation of an moving object will fluctuate in the same way as a moving point scatterer.
